---
title: "graphical_analysis"
date: "5/27/2021"
output: html_document
---

```{r}
library(tidyverse)
adults <- read.csv(here::here("data/adult.csv"), header = FALSE)

colnames(adults) <- c("age", "workclass", "fnlwgt", "education", "education_num", "marital_status",
                      "occupation", "relationship", "race", "sex", "capital_gain", "capital_loss",
                      "hoursper_week", "native_country", "income")
adults <- adults %>% 
  mutate(income = as.factor(income),
         workclass = as.factor(workclass),
         education = as.factor(education),
         marital_status = as.factor(marital_status),
         occupation = as.factor(occupation),
         relationship = as.factor(relationship),
         race = as.factor(race),
         sex = as.factor(sex),
         native_country = as.factor(native_country))
```


# Age and Income 
```{r}
adults %>%  
  ggplot(aes(x = age,
             color = income,
             fill = income)) + 
        geom_histogram() 
```
- Based on the graph above, you can see that both data tends to have a very right skewed data distributions. This is interesting as it also shows the participation to be much higher when the census taker is younger compared to the older. It is evident that the count of those that are making less than 50k a year is always larger than that of those that make more than 50k a year. 

# Marital Status and Income 
```{r}
adults %>%  
  ggplot(aes(fill = income, 
             x = marital_status)) + 
        geom_bar(position = "fill", width = .6) + 
        theme(axis.text = element_text(size = 6)) +
        labs(x = "Marital status", y = "Income")
```
 Based on the graph above, you can clearly see that the count of people who makes less than or equal to 50k a year is always larger than the count of people who makes more than 50k a year in all fields of marital status. And Married-AF-spouse and Married-civ-spouse has the most people who earn more than 50k per year.
 
# Education status and income 

```{r}
adults %>% 
  mutate(education = fct_relevel(education, " Preschool", " 1st-4th", " 5th-6th", " 7th-8th", " 9th", 
                                 " 10th", " 11th", " 12th", " HS-grad", " Assoc-voc", " Assoc-acdm", 
                                 " Some College", " Bachelors", "Prof-school", " Masters", " Doctorate")) %>% 
  ggplot(aes(fill = income,
             x = education)) +
  geom_bar(position = "fill") +
  theme(axis.text = element_text(size = 6)) +
  labs(x = "Education level", y = "Income")
```

We can see that people whose highest education level is preschool has 0% that earn more than 50k per year. And people who have higher education degree are more likely to have higher income.